---
title: "introR"
---



R can be used like a calculator
all regular operations apply
(), ^, *, /, +, -, and many more

"=" is meant as assignment, meaning everything on the righthand side is named whatever is on the left side. Whenver you call that name, you are using whatever was originally on the righthand side

```{r}
a = (1+2)/(3^2 * 5)
x = c(1,2,3,4,5,6,7,8)
```

Programming languages allow the creation of functions which allow the use of repeating a sequence of steps multiple times

```{r}
a_plus_b = function(a,b){
  a+b
}
a_plus_b(1,3)

a = seq(1,5)
a
b = rep(4, 5)
b

print("a")
a
print("b")
b

print("a+b")
c = a_plus_b(a,b)
print(c)

```

```{r}
combine = function(x, how){
  if(how =="add"){
    s = x[1]
    for(i in 2:length(x)){
      s = s +x[i]
    }
  }
  else if(how == "subtract"){
    s = x[1]
    for(i in 2:length(x)){
      s = s - x[i]
    }
    
  }
  if(how == "concatenate"){
    s = toString(x[1])
    for(i in 2:length(x)){
      s = paste(s, x[i],sep='')
        }
  }
  return(s)
  
}
x=c(1,2,3)
combine(x, how= "add")
combine(x, how="subtract")
combine(x, how="concatenate")

```
```


```{r}
compensation = read.csv("compensation.csv")
compensation
compensation$Grazing
```



We can plot this data using ggplot
```{r}
install.packages("ggplot2")
library(ggplot2)
?ggplot
?geom_point

names(compensation)
ggplot(data = compensation)+
  aes(x=Root, y=Fruit, color=Grazing)+
  geom_point(size=5)

```


Statistical functions 
```{r}
t.test(Fruit ~Grazing ,compensation)
```

```{r}
data(iris)

head(iris)
iris
setosa = iris[which(iris$Species=="setosa"),]
setosa

ggplot(data=setosa, aes(x= Sepal.Length, y= Sepal.Width))+
  geom_point()
```


